My title

### 2024-10-24 paper/paper.qmd
Update Result and Discussion parts; Modify Appendix B

Some of our data is of penguins (@fig-bills),

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

# #Interpretation of Coefficients:

@@

### Model justification

@@

## Predict and Combine with Electroal College to Predict

@@

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

## **Objective and Overview**
The goal of this survey methodology is to accurately forecast the outcome of the U.S. presidential election by collecting high-quality, representative data from a diverse set of respondents across the country. With a budget of $100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols. The approach is designed to maximize accuracy, reduce bias, and account for various demographic, geographic, and political factors that influence voting behavior.

### **Core Objectives**:
1. Obtain a representative sample of the U.S. electorate.
2. Ensure data quality through rigorous validation.
3. Leverage statistical modeling and poll aggregation for an accurate prediction.

## **1. Sampling Strategy**

The sampling strategy is designed to ensure that the survey reaches a broad, representative section of the voting population. To achieve this, we will use **stratified random sampling** combined with **quota sampling** for key demographics. This ensures that each important subgroup within the population is adequately represented.

### **Stratification Variables**:
- **Age Groups**: 18-29, 30-44, 45-64, 65+  
- **Gender**: Male, Female, Non-binary/Other  
- **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other  
- **Education Level**: No high school, High school graduate, College graduate, Post-graduate  
- **Income Bracket**: <$30,000, $30,000-$60,000, $60,000-$100,000, >$100,000  
- **Geographic Region**: Northeast, Midwest, South, West

**Sample Size**:  
A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1% at a 95% confidence level. This sample size will allow for detailed subgroup analysis (e.g., by state, demographic group), yielding statistically robust predictions.

**Weighting**:  
We will apply post-stratification weights to adjust for any oversampling or undersampling of specific demographic groups. For example, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.

## **2. Recruitment Strategy**

### **Recruitment Channels**:
To maximize respondent diversity and ensure accurate sampling, the survey will employ **multi-channel recruitment**:

- **Digital Advertisements**: Targeted ads on platforms like Facebook, Instagram, and Google will be used to recruit respondents based on their demographic profiles (age, gender, location, political interest). Custom audience features will be utilized to reach specific demographic and geographic groups.
- **Email Outreach**: If permissible, we will access voter registration databases and send email invitations to registered voters. This will allow us to target specific voter demographics that are harder to reach via digital ads.
- **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities (e.g., minority voter outreach programs) will further boost respondent diversity.
- **Incentives**: To increase response rates, each participant will be entered into a lottery with a chance to win a $100 gift card, encouraging broader participation.

## **3. Data Validation and Quality Assurance**

Maintaining data integrity and ensuring high-quality responses are critical to the accuracy of the election forecast. Therefore, several measures will be put in place to validate responses and reduce noise in the dataset.

### **Data Validation Protocols**:
1. **Real-time Captcha Verification**: This will prevent automated bots from submitting responses.
2. **Email/Phone Verification**: Respondents will verify their email or phone number to ensure authenticity. This ensures that each respondent only participates once.
3. **Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question. Responses completed suspiciously quickly (e.g., below 30% of the average completion time) will be flagged for review or exclusion.
4. **Voter Registration Cross-Check**: If feasible, respondents will be cross-referenced with voter registration records to ensure they are eligible to vote in the upcoming election.
5. **Response Audits**: Randomly selected respondents will be contacted to verify the accuracy of their responses, ensuring integrity in the dataset.

## **4. Poll Aggregation and Data Analysis**

### **Poll Aggregation**:
This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen our forecast through a **poll-of-polls** approach.

- **Weighting by Methodology and Recency**: Poll results will be weighted based on the rigor of their methodology (e.g., online vs. phone surveys, sample size) and the recency of the poll. Recent, methodologically sound polls will receive more weight in the aggregation process.
- **Handling Bias and Variability**: Aggregated results will adjust for pollster house effects (biases in methodology) and variability between polls, ensuring that no single poll dominates the prediction.

### **Modeling Approach**:
We will implement **Bayesian hierarchical models** to account for variability across different states, demographics, and regions. This will allow us to model the popular vote and potentially translate it into **Electoral College predictions**.

## **5. Budget Allocation**

- **Respondent Recruitment (Targeted ads, outreach)**: $70,000  
- **Incentives (e.g., lottery prizes)**: $10,000  
- **Survey Platform (Google Forms, Qualtrics subscription)**: $5,000  
- **Data Validation Tools**: $5,000  
- **Poll Aggregation & Analysis Software**: $10,000

@@

## **6. Survey Implementation**

The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection. The link to the live survey can be found here: [Google Form Survey](https://forms.gle/RC1464SvLvtoAYdv6). A copy of the questions is provided below.

@@

1. **Introduction**:
Thank you for taking part in this survey aimed at predicting the outcome of the 2024 US Presidential election. Your insights are valuable to our research.

Please note:
- **All responses will be kept strictly confidential.**
- **Your participation is entirely voluntary.**
- **We kindly request that you answer all questions honestly and to the best of your knowledge.**
- **The survey is estimated to take approximately 10 minutes to complete.**
If you have any inquiries or concerns regarding this survey, please don't hesitate to contact the research team at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca).

@@

2. **Section 1: Eligibility Screening**:
Are you a U.S. citizen?
- Yes
- No [If No, end survey]

@@

3. **Section 2: Demographic Information**:
What is your age group?
- 18-29
- 30-44
- 45-64
- 65 or older
- Prefer not to say

@@

4. **Section 3: Political Views and Voting Intentions**:
How likely are you to vote in the 2024 Presidential election?
- Definitely will vote
- Probably will vote
- Might or might not vote
- Probably will not vote
- Definitely will not vote

@@

5. **Section 4: Information Sources and Engagement**:

@@

6. **Section 5: Validation and Consent**:
Please verify that you are a human by selecting "Blue" from the following options:
- Red
- Green
- Blue
- Yellow

@@

7. **End Message**:
"Thank you for completing this survey. Your response has been recorded.
If you have any questions about this survey or would like to be informed about the results, please contact [Your Contact Information]."

@@

### **7. Survey Design Considerations**

- **Question Wording**: All questions are carefully designed to avoid bias or leading responses.
- **Neutrality**: Political questions are framed neutrally to avoid pushing respondents toward specific answers.
- **Pilot Testing**: Before full deployment, the survey will undergo a pilot test to identify and resolve any issues.

This methodology, combining rigorous sampling, data validation, and aggregation, ensures that the election forecast is as accurate and representative as possible.

>>>>>>> 7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4

>>>>

Some of our data is of penguins (fig-bills),

@@

And also planes (fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix @sec-model-details].

@@

## Interpretation of Coefficients:

@@

## Model justification

@@

## Predicted Electoral Outcomes
We applied a regression model to predict the percentage of votes Trump is expected to receive in each state. The model results, combined with each state's electoral vote allocation, allowed us to predict the winner in each state. Based on this, we calculated the total number of electoral votes for both Trump and Harris.

The table below (@tbl-prediction) summarizes the predicted results, showing Trump’s predicted percentage, the number of electoral votes in each state, and the predicted winner (either Trump or Harris). For instance:
- Alabama: Trump is predicted to win 53% of the vote, securing all 9 electoral votes.
- California: Trump is predicted to receive 34.39% of the vote, resulting in a victory for Harris, who takes California's 55 electoral votes.
- Florida: The model predicts a close race, with Trump at 48.89% of the vote, resulting in a Harris win in this critical battleground state.

Electoral Vote Count:
- Trump Electoral Votes: 78
- Harris Electoral Votes: 416
These results indicate that based on the current model predictions, Harris is expected to win the 2024 U.S. Presidential Election, securing 416 electoral votes, compared to Trump’s 78 electoral votes. The election outcome hinges on several battleground states, where the vote margins are predicted to be narrow.

@@

## Predicted Electoral Outcomes by State
The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S. Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
#| echno: false
#| label: fig-statemap
#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false
#| 
# Load necessary libraries
library(usmap)

# "red" for Trump and "blue" for Harris
state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "red", "blue")

# Create a map visualization showing the predicted winner by state
plot_usmap(data = state_predictions, values = "winner_color", regions = "states") +
  scale_fill_manual(values = c("red" = "red", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
  labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
  theme(legend.position = "right")

```
The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois. However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.

# Discussion {#sec-discussion}

## What Is Done in This Paper?
This paper uses a regression model to predict the outcome of the 2024 U.S. Presidential Election between Donald Trump and Kamala Harris. By analyzing historical voting data, the model forecasts the percentage of votes Trump is expected to receive in each state. These predictions are combined with the state's electoral vote allocation to determine the overall winner. The findings indicate a significant electoral victory for Harris, projecting 416 electoral votes for her compared to 78 for Trump. A geographic map is also presented to visualize state-level outcomes and highlight regional voting trends.

## What Do We Learn About the World?
The study highlights the persistence of geographic voting patterns in U.S. elections. Even with changes in candidates, many states follow their historical voting tendencies. Republican-leaning states like Alabama and Wyoming are projected to support Trump, while Democratic-leaning states such as California and New York favor Harris. This pattern shows the strong influence of regional political loyalties, which continue to shape election outcomes.

## Another Thing We Learn About the World
The analysis underscores the importance of battleground states in determining the election's outcome. States like Florida and Arizona, predicted to lean toward Harris, play a decisive role in the projected electoral victory. This illustrates how close contests in a few states can influence the overall election result, emphasizing the significant impact these states have in shaping the presidency.

## Weaknesses of What Was Done
While the model offers a useful prediction, it has limitations. It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election. The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts. Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape.

## What Is Left to Learn or How Should We Proceed in the Future?
Future research should incorporate more detailed data, including demographic shifts and economic factors that may influence voter preferences. It would be valuable to examine how emerging political movements and changes in communication strategies affect elections, particularly in closely contested states. Post-election analysis comparing predictions with actual results will also be essential to improving the accuracy of models and understanding how unforeseen events may alter outcomes.

## Weaknesses and next steps
The logistic regression model is limited by the lack of interaction terms between states, which may obscure regional trends or external factors that influence neighboring states. Additionally, the model assumes that polling data accurately reflects voter intentions, but biases or missing data in key regions could affect the predictions.

Future iterations of this model should incorporate voter turnout predictions, demographic variables, and real-time polling updates to better capture the dynamics of voter behavior. Including social media sentiment analysis and analyzing cross-state interactions could refine the prediction model, offering more nuanced insights into election forecasts.

@@

## Objective and Overview
The goal of this survey methodology is to accurately forecast the outcome of the U.S. presidential election by collecting high-quality, representative data from a diverse set of respondents across the country. With a budget of \$100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols. The approach is designed to maximize accuracy, reduce bias, and account for various demographic, geographic, and political factors that influence voting behavior.

## Core Objectives
* Obtain a representative sample of the U.S. electorate.
* Ensure data quality through rigorous validation.
* Leverage statistical modeling and poll aggregation for an accurate prediction.

## Sampling Strategy
The sampling strategy is designed to ensure that the survey reaches a broad, representative section of the voting population. To achieve this, we will use **stratified random sampling** combined with **quota sampling** for key demographics. This ensures that each important subgroup within the population is adequately represented.

### Stratification Variables
* **Age Groups**: 18-29, 30-44, 45-64, 65+ 
* **Gender**: Male, Female, Non-binary/Other 
* **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other 
* **Education Level**: No high school, High school graduate, College graduate, Post-graduate 
* **Income Bracket**: <$30,000, \$30,000-\$60,000, \$60,000-\$100,000, >\$100,000 
* **Geographic Region**: Northeast, Midwest, South, West

### Sample Size
A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1\% at a 95\% confidence level. This sample size will allow for detailed subgroup analysis (e.g., by state, demographic group), yielding statistically robust predictions.

### Weighting
Post-stratification weights will be applied to adjust for any oversampling or undersampling of specific demographic groups. For example, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.

## Recruitment Strategy
To maximize respondent diversity and ensure accurate sampling, the survey will employ **multi-channel recruitment**:

* **Digital Advertisements**: Targeted ads on platforms like Facebook, Instagram, and Google will recruit respondents based on their demographic profiles (age, gender, location, political interest).
* **Email Outreach**: If permissible, voter registration databases will be accessed to send email invitations to registered voters.
* **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities will further boost respondent diversity.
* **Incentives**: Each participant will be entered into a lottery with a chance to win a \$100 gift card to encourage participation.

## Data Validation and Quality Assurance
Maintaining data integrity and ensuring high-quality responses are critical to the accuracy of the election forecast. Several measures will be put in place to validate responses and reduce noise in the dataset.

### Data Validation Protocols
* **Real-time Captcha Verification**: This will prevent automated bots from submitting responses.
* **Email/Phone Verification**: Respondents will verify their email or phone number to ensure authenticity and prevent duplicate submissions.
* **Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question. Responses completed suspiciously quickly will be flagged for review.
* **Voter Registration Cross-Check**: If feasible, respondents will be cross-referenced with voter registration records to ensure eligibility.
* **Response Audits**: Randomly selected respondents will be contacted to verify the accuracy of their responses, ensuring dataset integrity.

## Poll Aggregation and Data Analysis
### Poll Aggregation
This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach.

* **Weighting by Methodology and Recency**: Poll results will be weighted based on the rigor of their methodology and the recency of the poll.
* **Handling Bias and Variability**: Aggregated results will adjust for pollster biases and variability between polls to ensure that no single poll dominates the prediction.

### Modeling Approach
**Bayesian hierarchical models** will account for variability across different states, demographics, and regions. This will allow for modeling the popular vote and potentially translating it into **Electoral College predictions**.

## Budget Allocation
* **Respondent Recruitment (Targeted ads, outreach)**: \$70,000
* **Incentives (e.g., lottery prizes)**: \$10,000
* **Survey Platform (Google Forms, Qualtrics subscription)**: \$5,000
* **Data Validation Tools**: \$5,000
* **Poll Aggregation \& Analysis Software**: \$10,000

@@

## Survey Implementation
The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection. You can access the survey at the following link: [Google Form Survey](https://forms.gle/XxtMTMc45d6VzNuy8)

@@

\begingroup
\small
**Introduction**:

Thank you for taking part in this survey aimed at predicting the outcome of the 2024 US Presidential election. Your insights are valuable to our research.

Please note:

- **All responses will be kept strictly confidential.**
- **Your participation is entirely voluntary.**
- **We kindly request that you answer all questions honestly and to the best of your knowledge.**
- **The survey is estimated to take approximately 10 minutes to complete.**

If you have any inquiries or concerns regarding this survey, please don't hesitate to contact the research team at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca).(Yuxuan Wei, Xuanle Zhou, Yongqi Liu)

@@

**Section 1: Eligibility Screening**:

Are you a U.S. citizen?
- Yes
- No [If No, end survey]

@@

**Section 2: Demographic Information**:

What is your age group?
- 18-29
- 30-44
- 45-64
- 65 or older
- Prefer not to say

@@

**Section 3: Political Views and Voting Intentions**:

How likely are you to vote in the 2024 Presidential election?
- Definitely will vote
- Probably will vote
- Might or might not vote
- Probably will not vote
- Definitely will not vote

@@

**Section 4: Information Sources and Engagement**:

@@

**Section 5: Validation and Consent**:

Please verify that you are a human by selecting "Blue" from the following options:
- Red
- Green
- Blue
- Yellow

@@

**End Message**:

"Thank you for completing this survey. Your response has been recorded.
If you have any questions about this survey or would like to be informed about the results, please contact at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca)."

\endgroup

@@

## Survey Design Considerations
* **Question Wording**: All questions are designed to avoid bias or leading responses.
* **Neutrality**: Political questions are framed neutrally to avoid influencing respondents' answers.
* **Pilot Testing**: The survey will undergo a pilot test to identify and resolve any issues before full deployment.
